Verifying Cache Coherence Protocols for an infinite family of cache hierarchies

### 2014-02-06 paper/Introduction.tex
Fix missing citation

Formal verification of cache coherence protocols has traditionally been done
using model-checking based approaches. This signficantly restricts the size as
well as complexity of the system that has to be verified; most model-checking
based approaches can not handle more than one level of hierarchy. To the best
of our knowledge, the largest system that has been verified using
model-checking based approaches has only 12 processors. \xxx{citation:
http://www.cs.utah.edu/formal\_verification/pdf/xiaofang\_dissertation.pdf (used
data from their related work must cite)}.

>>>>

Formal verification of cache coherence protocols has traditionally been done
using model-checking based approaches. This signficantly restricts the size as
well as complexity of the system that has to be verified; most model-checking
based approaches can not handle more than one level of hierarchy. To the best
of our knowledge, the largest system that has been verified using
model-checking based approaches has only 12 processors~\cite{Chen:2008:VHC:1559300}.
